\documentclass{llncs}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{url}
\usepackage{listings, tikz}
\usetikzlibrary{positioning,shapes}
\usepackage{verbatimbox}

\newtheorem{Definition}{Definition}
\newtheorem{Theorem}{Theorem}
\newtheorem{Lemma}{Lemma}
\newtheorem{Property}{Property}
\newtheorem{Corollary}{Corollary}
\newtheorem{Proof}{Proof}

\renewcommand{\ttdefault}{pcr}

\lstset{language=Java,
	breaklines=true,
	%basicstyle=\small,
	basicstyle=\ttfamily\footnotesize,
	keywordstyle=\bfseries,
	numbers=left,numberstyle=\scriptsize,
	columns=fullflexible, keepspaces=true,
	%numbers=left,numberstyle=\scriptsize
	%numbers=left,numberstyle=\tiny
	%frame=single
}

\newcommand{\mathword}[1]{{\tt \mathit{#1}}}
\newcommand{\mw}[1]{\mathword{#1}}
\newcommand{\keyword}[1]{\mathsf{#1}}
\newcommand{\kw}[1]{\keyword{#1}}
\newcommand{\ruledef}[3]{ $\frac{\begin{array}[c]{c}{ \rulename{#1}}\\ #2 \end{array}}{\begin{array}[c]{c}#3\end{array}}$}
\newcommand{\ruledefN}[2]{ $\frac{\begin{array}[c]{c} #1 \end{array}}{\begin{array}[c]{c}#2\end{array}}$}
\newcommand{\ruledefX}[2]{ $\begin{array}[c]{c} \rulename{#1}\\ #2 \end{array}$}
\newcommand{\rulename}[1]{{\scriptsize\textsc{[\MakeUppercase{#1}]}}}
\newcommand{\rn}[1]{\rulename{#1}}
\newcommand{\textcode}[1]{\lstinline|#1|}
\newcommand{\tc}[1]{\lstinline|#1|}

\newcommand{\Reducesto}[0]{ \ \Downarrow \ }
\newcommand{\equalson}[1]{ \ \stackrel{#1}{=} \ }
\newcommand{\approxon}[1]{ \ \stackrel{#1}{\approx} \ }
\newcommand{\simon}[1]{ \ \stackrel{#1}{\sim} \ }

\newcommand{\kwnull}[0]{\keyword{null}}
\newcommand{\kwnew}[0]{\keyword{new}}
\newcommand{\kwextends}[0]{\keyword{extends}}
\newcommand{\kwclass}[0]{\keyword{class}}
\newcommand{\kwthis}[0]{\keyword{this}}
\newcommand{\kwif}[0]{\keyword{if}}
\newcommand{\kwthen}[0]{\keyword{then}}
\newcommand{\kwelse}[0]{\keyword{else}}
\newcommand{\kwskip}[0]{\keyword{skip}}

\newcommand\Var{\mathtt{VAR}}
\newcommand\Val{\mathtt{V}}
\newcommand\Obj{\mathtt{OBJ}}

%%% The key relations

\newcommand{\VPT}{\Omega}
\newcommand{\HPT}{\Phi}
\newcommand{\Class}{\mathcal{C}}
\newcommand{\Field}{\mathcal{F}}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\word}[1]{\langle #1\rangle}
\newcommand{\Nat}{\mathbb{N}}
\newcommand{\less}{\sqsubseteq}
\newcommand{\tflow}{\dashrightarrow}
\newcommand{\hflow}{\rightarrow}
\newcommand{\lhflow}[1]{\stackrel{#1}{\hflow}}

\newcommand\Loc{\mathcal{L}}
\newcommand\Label{\Phi}
\newcommand\set[1]{\{#1\}}
\newcommand\power{\mathcal{P}}
\newcommand\join{\cup}
\newcommand\subtype{\subseteq}

\title{A Relational Static Semantics for Call Graph Resolution}
\author{\today}
\institute{Jinan University}

\begin{document}

\maketitle

\abstract{The problem of resolving virtual method and interface calls in Object-Oriented languages has been a long standing challenge to the program analysis community. In this paper, we propose a new approach called type flow analysis that represent the propagation of type information between program variables by a group of relations without the help of a heap abstraction. We prove that regarding the precision on reachability of class information to variables, our method produces results equivalent to that one can derive from a points-to analysis. Moreover, in practice, our method consumes lower time and space usage, as supported by the experimental results.
}

\section{Experiment}\label{sec:experiment}
We evaluated our approach by measuring its performance in terms of generated callsites and runtime on 13 benchmark test cases. \textit{Compress}, \textit{crypto} are from the SPECjvm2008 suite, and the rest of those are from the Dacapo suite. We randomly selected these test cases based on its size increasing.
All of our experiments were conducted on an Intel i5-8250U processor at 1.60 GHz and 8 GB memory running Ubuntu 16.04LTS, with the Openjdk 1.8.0.

We compared our approach against CHA and PTA implemented by Soot, the most popular static analysis framework for Java. We run context-insensitive PTA because our approach is context-insensitive, thus results will be more comparable.

\textbf{Efficiency:}As shown in Table~\ref{experiment:Time Cost}, our approach is more efficient than PTA, and generally more efficient than CHA, especially when the program callsite increasing. Time cost in our approach is basically depending on the size of generated relations. More specifically, most of the time is consumed to calculate the fixpoint. For example, CHA, PTA analyze the benchmark \textit{bootstrap} about 23.74 and 34.13 seconds, respectively. TFA only excutes about 0.029 second. The reason is mostly because the relations only reach to 661 in total. There are 3 benchmarks, \textit{xalan, antlr, batik}, can not be analyzed by PTA because it raise the jvm GC overhead limit error, so we put the label "N/A" in Table~\ref{experiment:Time Cost}

\begin{table}[!htbp]\centering
\caption{Time cost with different analysis}
\begin{tabular}{lcccccc}
	\hline
	\textbf{bench} & \textbf{T$_{cha}(s)$} & \textbf{T$_{pta}(s)$} & \textbf{T$_{tfa}(s)$} & \textbf{R$_{type}$} & \textbf{R$_{\less}$} & \textbf{R$_{\lhflow{f}}$} \\
	\hline
	compress & 0.02 & 0.12 & 0.013 & 87 & 202 & 24\\
	crypto & 0.01 & 0.12 & 0.028 & 94 & 226 & 18\\
	bootstrap & 23.74 & 34.13 & 0.029 & 191 & 453 & 17\\
	commons-codec & 0.009 & 0.12 & 0.131 & 306 & 3324 & 49\\
	junit & 24.45 & 34.24 & 0.153 & 1075 & 5772 & 245\\
	commons-httpclient & 0.009 & 0.12 & 0.362 & 2423 & 8511 & 597 \\
	serializer & 22.60 & 32.68 & 1.704 & 3006 & 17726 & 368\\
	xerces & 21.69 & 34.83 & 3.434 & 12590 & 72503 & 3660\\
	eclipse & 21.95 & 42.64 & 1.671 & 7933 & 37435 & 2078\\
	derby & 22.77 & 48.82 & 17.781 & 20698 & 191854 & 6236\\
	xalan & 78.40 & N/A & 28.901 & 32971 & 162249 & 4438\\
	antlr & 44.20 & N/A & 3.73 & 16117 & 76741 & 6014\\
%	jython & 3811.02 & / & /  & / \\
	batik & 45.84 & N/A & 5.031 & 29409 & 122534 & 9569 \\
	\hline
\end{tabular}
\label{experiment:Time Cost}
\end{table}

\textbf{Accurancy:}We consider generated callsite as the aspect of accurancy. Table~\ref{experiment:Callsite} shows the callsite generated by different analysis. We calculate the origin callsite, the callsite directly written in source code, as the baseline. Our approach reduces a satisfying number of callsite, yielding corresponding accurancy. The result is comparable to what can be achieved by the points-to analysis.

\begin{table}[!htbp]\centering
\caption{Optimalization result}
\begin{tabular}{lcccc}
	\hline
	\textbf{bench} & \textbf{Node$_{origin}$} & \textbf{Node$_{opt}$} & \textbf{Reduce} & \textbf{Time$(s^{-1})$} \\
	\hline
	compress & 205 & 130 & $36.59\%$ & 0.008 \\
	crypto & 312 & 158 & $49.36\%$ & 0.010 \\
	bootstrap & 514 & 279 & $45.72\%$ & 0.023 \\
	commons-codec & 1742 & 886 & $49.14\%$ & 0.189 \\
	junit & 5859 & 3243 & $44.65\%$ & 2.301 \\
	commons-httpclient & 9708 & 5168 & $46.77\%$ & 4.873 \\
	serializer & 9600 & 6671 & $30.51\%$ & 3.416 \\
	xerces & 41634 & N/A & N/A & N/A\\
	eclipse & 34631 & N/A & N/A & N/A\\
	derby & 112265 & N/A & N/A & N/A\\
	xalan & 103697 & N/A & N/A & N/A\\
	antlr & 56589 & N/A & N/A & N/A\\
%	jython & / & / & / & /\\
	batik & 89336 & N/A & N/A & N/A\\
	\hline
\end{tabular}
\label{experiment:Optimalization}
\end{table}

\textbf{Optimazation:}We use a split algorithm to merge the node that have the same behavior. Thus we can reduce the space. The results are showed in Tabel~\ref{experiment:Optimalization}. We evaluated our optimazation algorithm on all benchmarks and sucessfully exceute our approach on 7 benchmarks. It shows that we can reduce the space by about 45$\%$ on average, with a reasonable time consuming. Another 6 benchmarks can not be execute because the same reason metioned above with PTA. We put the label "N/A" on Table~\ref{experiment:Optimalization}.  

\begin{table}[!htbp]\centering
\caption{Callsite generated with different analysis}
\begin{tabular}{lcccc}
	\hline
	\textbf{bench} & \textbf{CS$_{origin}$} & \textbf{CS$_{cha}$} & \textbf{CS$_{pta}$} & \textbf{CS$_{tfa}$} \\
	\hline
	compress & 153 & 160 & 18 & 73 \\
	crypto & 302 & 307 & 62 & 121 \\
	bootstrap & 657 & 801 & 891 & 328 \\
	commons-codec & 1162 & 1372 & 270 & 442 \\
	junit & 3196 & 17532 & 11176 & 1358 \\
	commons-httpclient & 6817 & 17118 & 567 & 2927 \\
	serializer & 4782 & 9533 & 1248 & 1756 \\
	xerces & 24579 & 56252 & 10631 & 8111 \\
	eclipse & 23607 & 95073 & 70016 & 9379 \\
	derby & 69537 & 180428 & 85212 & 16381 \\
	xalan & 57430 & 155866 & N/A & 18669 \\
	antlr & 62007 & 147014 & N/A & 17177 \\
%	jython & 129332 & 466167 & / & /  \\
	batik & 56877 & 235071 & N/A & 20901 \\
	\hline
\end{tabular}
\label{experiment:Callsite}
\end{table}


\bibliographystyle{plain}
\bibliography{literature}
\end{document}
